### 2023-12-26 sections/5-discussion.tex
more changes to discussion

We also note that on different datasets which exhibit manifold structures, the highest-throughput CAKES algorithm varies. 
For example, on Glove-25, Repeated $\rho$-NN exhibits the highest throughput of any CAKES algorithm, despite having the lowest throughput of the three on Sift and Fashion-mnist. 
On Silva,  Repeated $\rho$-NN is comparable to the other CAKES algorithms at low multipliers, but becomes the best of the three at higher multipliers. 
When we view these results in light of the LFD plots in Section~\ref{subsec:lfd-results}, we realize that  Repeated $\rho$-NN appears to be the best-performing CAKES algorithm on datasets where a large proportion of the dataset has a very low LFD (i.e., near 2), like Glove-25 and Silva. 
This general trend is unsurprising, given that Repeated $\rho$-NN relies on a low LFD around the query in order to quickly home in on the correct radius for $k$ hits. 
While it varies which of the two algorithms has better throughput, we observe that on all three ANN benchmark datasets (Fashion-mnist, Glove-25, and Sift), GreedySieve's and Sieve's throughput stays nearly constant as the cardinality multiplier increases. 
This observation warrants further investigation, but it is especially promising given that GreedySieve and Sieve consistently outperform linear search for high cardinalities. 
Finally, we emphasize that the variation in performance of our algorithms across different datasets and cardinalities support our use of an auto-tuning function (as discussed in Section~ref{subsec:methods:auto-tuning}) to select the best choice of algorithm for a given dataset. 
Given the trends such as that with low LFD and Repeated $\rho$-NN's performance, we suspect that a more sophisticated, less-heuristic auto-tuning function could be developed to select the best algorithm based on the properties of the dataset.

@@

% Is this still true: "However, the ann-benchmarks results show that even when FAISS and HNSW are tuned for lower recall, they are still slower than CAKES in all cases."

>>>>

We also note that on different datasets which exhibit manifold structures, the highest-throughput CAKES algorithm varies. 
For example, on Glove-25, Repeated $\rho$-NN exhibits the highest throughput of any CAKES algorithm, despite having the lowest throughput of the three on Sift and Fashion-mnist. 
On Silva,  Repeated $\rho$-NN is comparable to the other CAKES algorithms at low multipliers, but becomes the best of the three at higher multipliers. 
When we view these results in light of the LFD plots in Section~\ref{subsec:lfd-results}, we realize that  Repeated $\rho$-NN appears to be the best-performing CAKES algorithm on datasets where a large proportion of the dataset has a very low LFD (i.e., near 2), like Glove-25 and Silva. 
This general trend is unsurprising, given that Repeated $\rho$-NN relies on a low LFD around the query in order to quickly home in on the correct radius for $k$ hits. 
These findings suggest that Repeated $\rho$-NN is the most ``sensitive'' to the manifold structure of the dataset. 
Exploring this sensitivity is a potential avenue for future investigation, as it remains to determine at what LFD value Repeated $\rho$-NN transitions from being the best-throughput CAKES algorithm to being the worst-throughput CAKES algorithm, and whether this transition is sharp.

While the algorithm with best throughput varies, we observe that on all three ANN benchmark datasets (Fashion-mnist, Glove-25, and Sift), GreedySieve's and Sieve's throughput stays nearly constant as the cardinality multiplier increases. 
This observation warrants further investigation, but it is especially promising given that GreedySieve and Sieve consistently outperform linear search for high cardinalities. 
Finally, we emphasize that the variation in performance of our algorithms across different datasets and cardinalities support our use of an auto-tuning function (as discussed in Section~ref{subsec:methods:auto-tuning}) to select the best choice of algorithm for a given dataset. 
Given the trends such as that with low LFD and Repeated $\rho$-NN's performance, we suspect that a more sophisticated, less-heuristic auto-tuning function could be developed to select the best algorithm based on the properties of the dataset.

@@
